Can Communication Protocols Find Small LPs?

### 2019-04-05 CS860-CommunicationComplexity/project/presentation.tex
Slides drafted

\begin{document}

\maketitle

\begin{frame}{A First Slide}
\end{frame}
\end{document}

>>>>

\begin{document}
\setbeamercolor{background canvas}{bg=white}
\maketitle

\begin{frame}{The Min Knapsack Problem}
Given $n$ \alert{items} with individual \alert{sizes}, $s_i$, and \alert{costs}, $c_i$, for $i \in [n]$.
\vfill
Also given a \alert{demand} $D$. \onslide<2->{Want to compute the \alert{Min Knapsack}

\begin{align*}
\min\ &\sum_{i\in [n]} c_i x_i \\
\text{s.t.} &\sum_{i \in [n]} s_i x_i \geq D \\
&x \in \{0,1\}^n.
\end{align*}}
\vfill\onslide<3->{
Standard Linear Programming relaxation has an \alert{unbounded integrality gap.}}
\end{frame}

\begin{frame}{Knapsack Cover Inequalities}
LP relaxation can be \alert{strengthened} to an integrality gap of $2$ by adding all \alert{Knapsack Cover Inequalities}.
\vfill\onslide<2->{
\textbf{Knapsack Cover Inequality:} for $B\subseteq [n]$, the inequality of the form 
$$\sum_{i \in [n]\backslash B} s_i(B) x_i \geq D(B),$$
where $D(B) = \max\{D-\sum_{i\in B} s_i, 0\}$ and $s_i(B) = \min\{s_i, D(B)\}.$}
\vfill\onslide<3->{
\textbf{Big Open Question:} Is there a \alert{polynomial size formulation} for Knapsack Cover LP?}
\end{frame}
\begin{frame}{Extended Formulations}
    \begin{columns}
        \begin{column}{0.4\textwidth}
    \begin{figure}
        \includegraphics[scale=0.075]{std_ex.png}
    \end{figure}
\end{column}
\begin{column}{0.6\textwidth}\onslide<2->{
\textbf{Extension Complexity:} $xc(P) :=$ Min \alert{number of facets} to describe polytope $P $ as the projection of a \alert{higher dimensional polyhedron.}}
\vfill\onslide<3->{
\textbf{Theorem:} (Yannakakis) $xc(P) = \Theta(\text{rk}_+(S))$ where $S$ is a \alert{slack matrix} of $P$, and $\text{rk}_+$ denotes non-negative rank.}
\end{column}
\end{columns}
\vfill\onslide<4->{
\alert{Knapsack Cover:} the slack matrix has entries 
$$ S_{A,B} = \sum_{i \in A\backslash B} s_i(B) - D(B)$$
for knapsack solution $A$, and $B\subseteq [n]$.}
\end{frame}
\begin{frame}{Communication Protocols for the Slack Matrix}
Consider communication problem for $S : \{\text{Knapsacks}\}\times [n] \rightarrow \Z_{\geq 0}$.
\vfill\onslide<2->{
We say \alert{private random} communication protocol $\pi$ computes $S$ in \alert{expectation} if
$$\mathbb{E}[\pi(A,B)] = S_{A,B}$$
for all $(A,B) \in \text{domain}(S)$.}
\vfill\onslide<3->{
\textbf{Theorem:} (Faenza, Fiorini, Grappe, Tiwary) $$\min_\pi(\text{cost}(\pi)) = \log(\text{rk}_x(S)) + \Theta(1) = \log(xc(P)) + \Theta(1)$$}
\end{frame}
\begin{frame}{Results}
\textbf{Theorem:} (Bazzi, Fiorini, Huang, Svensson) There is a protocol which computes $S$ in expectation with cost $O(\log^2(n))$.
\vfill
\hrule
\vfill\onslide<2->{
\textbf{Goal:} Provide \alert{non-trivial lower bounds} on communication protocols computing $S$ in expectation.}
\vfill\onslide<3->{
\textbf{Lemma:} (T.) If protocol $\pi$ uses \alert{$O(1)$ bits of randomness} to compute $S$ in expectation then $\text{cost}(\pi) = \Omega(n)$.}
\vfill\onslide<4->{
\textbf{Lemma:} (T.)  Let $R$ be the set of \alert{one-way} protocols where \alert{only Alice} has private randomness, which compute $S$ in expectation. Then $$\min_{\pi\in R}(\text{cost}(\pi)) = \log(\text{rk}_x(S)) + \Theta(1).$$}
\end{frame}
\end{document}
